\chapter{Resources \& Risks}
\label{ch:resources_and_risks}
This project will primarily rely on standard software and accessible high-performance computing hardware owned by the Department of Computer Science. In particular, I refer to the DCS Batch Compute system for more intensive simulations, especially those leveraging noise models mentioned earlier \cite{king2002capacityquantumdepolarizingchannel}.

For initial development and small-scale simulations, I will perform these on a personal Macbook M3 Pro. I will also leverage free cloud-based access to real quantum hardware provided by IBM \cite{ibm-quantum}, which at the time of writing grants open-plan users a set amount of free execution time on their devices per month to run small-scale onstances of the selected protocol on real Noisy Intermediate-Scale Quantum (NISQ) devices. This will offer a valuable insight into the difference between simulated noise models and real-world hardware performance. It is possible that IBM revokes access to their real NISQ devices for free, but it is only a nice-to-have of the project rather than its central focus - therefore not a large risk.

A number of books and and papers will also be reviewed throughout the course of this project (\cite{https://doi.org/10.4230/lipics.itcs.2024.24}, \cite{caro2025interactiveproofsverifyingquantum}, \cite{aharonov2017interactiveproofsquantumcomputations}, to begin with) but all materials used in future will be properly referenced in the following reports. I will also keep regular, biweekly communication going with my supervisor, Dr. Matthias Caro, as well as get in touch other students in the field.

It is also possible that finding changes to make to quantum protocols becomes infeasible after thorough investigation (possibly due to mathematical or practical complexity). In this case, I will be able to back up the conclusion with empirical and theoretical evidence of work, as well as contribute a larger number of implementations on quantum interactive proof protocols that have not yet been explored.
